Propositions as Sessions, Mechanically

### 2015-04-11 paper/formalisation.tex
Added Wadler let rule version.

\input{gv}

The typing judgements for the functional language GV are shown in
Figure~\ref{fig:gv}. Note that I have altered the $n$-ary branch and choice
constructs to the restricted binary versions in order to avoid tricky
formulations. The change is not restrictive however, since CP itself provides
only binary versions of plus ($\oplus$) and with ($\with$)
constructs. Explicit limiting and unlimiting of abstraction was chosen to
enable the inclusion of these rules in the translation from GV to CP, which is
performed by induction on GV terms. \todo{could take about opening the
  multiple binder let. multi but not as in literature}

>>>>

\input{gv}
\input{letscompare}

The typing judgements for the functional language GV are shown in
Figure~\ref{fig:gv}. Note that I have altered the $n$-ary branch and choice
constructs to the restricted binary versions in order to avoid tricky
formulations. The change is not restrictive however, since CP itself provides
only binary versions of plus ($\oplus$) and with ($\with$)
constructs. Explicit limiting and unlimiting of abstraction was chosen to
enable the inclusion of these rules in the translation from GV to CP, which is
performed by induction on GV terms and is therefore
syntax-directed. Figure~\ref{fig:letscompare} presents the informal version of
the well-typed let rule. While \citeauthor{Char:2012} suggests a two-indices
approach for handling for multiple binders~\cite{Char:2012}, such a strategy
seems excessive for the GV let rule and the only rule to benefit from multiple
binders. For that reason, the simple solution of performing two openings was
chosen.
